\section{Related Work}
\label{sec:related_work}

\paragraph{Chain-of-thought and self-consistency.}
Chain-of-thought (CoT) prompting \citep{wei2022chain} and its zero-shot variant \citep{kojima2022large} demonstrated that step-by-step reasoning elicits substantially stronger performance from large language models on mathematical and logical tasks.
Building on CoT, \citet{wang2023self} introduced self-consistency, in which multiple reasoning paths are sampled and the most frequent final answer is returned.
Self-consistency is a direct ancestor of the exploration strategy in this work: the frontier method accumulates a pool of candidate answers via diverse sampling before applying a selection policy.
The key difference from self-consistency is that our selection policy is conditioned on logged execution metadata---specifically failure-trace signals from the frontier run---rather than raw majority vote across all samples.

\paragraph{Test-time compute scaling.}
Recent work has shown that scaling inference-time computation can yield accuracy gains comparable to scaling model parameters \citep{snell2024scaling}.
Budget-forcing \citep{muennighoff2025s1} operationalises this by extending or truncating the reasoning trace to a target token count, encouraging the model to use its full compute allotment.
\citet{wu2024inference} and related work study cost--performance trade-offs across test-time strategies (for example, sampling, voting, and search variants) under fixed compute budgets.
The present work occupies a complementary niche: given candidate answers generated under a common per-method budget cap (budget~$= 6$ in our setting), we ask how to select the best answer from the available pool without additional generation.

\paragraph{Tree-structured and search-based reasoning.}
Tree of Thoughts \citep{yao2023tree} and similar frameworks \citep{besta2024graph} extend CoT to multi-branch deliberate search, where the model evaluates partial solutions at each step.
These approaches improve coverage of the solution space at the cost of increased inference computation.
The frontier method used as our baseline can be viewed as a lightweight variant: it generates candidates via program-aided execution \citep{gao2023pal}, accumulates a diverse pool under a budget constraint, and selects a final answer via a fixed rule.
The failure modes we identify---structurally weak single-branch explorations and frontier-external disagreements---arise specifically because not all budget allocations produce equally reliable candidates, motivating the gating rules in FIX-2 and FIX-4.

\paragraph{Verifier-guided reranking and outcome reward models.}
A complementary line of work trains separate verifier or reward models to rerank candidate solutions.
\citet{cobbe2021training} showed that a trained outcome verifier substantially improves answer selection on the GSM8K benchmark.
Process reward models \citep{lightman2024lets} extend this to step-level verification, providing finer-grained feedback.
In our setting, a SetFit verifier \citep{tunstall2022efficient} was trained during the RelationReady phase and showed positive within-method reranking signal; however, cross-method routing was method-entangled and not promoted.
The gating rules studied in this paper avoid learned verifier components entirely: they rely only on runtime metadata that is logged as a side-effect of the frontier run.

\paragraph{Cost-aware routing and cascades.}
FrugalGPT \citep{chen2023frugalgpt} and related cascade approaches \citep{dohan2022language} route queries to cheaper models or early-exit points when a confidence threshold is met.
These methods reduce overall inference cost by skipping expensive models on ``easy'' examples.
Our setting differs in that each candidate-producing method is evaluated under the same budget contract: no compared method receives a larger per-example call cap, and the selection policy itself issues no calls.
The allocation question is therefore not which model to call, but which answer to surface from an already-generated candidate pool, given only gold-free execution signals.

\paragraph{Prompt-budget strategies.}
Several approaches directly manipulate the prompt or generation parameters to control inference cost.
TALE-style prompt budgeting, used as an external baseline in this paper, allocates a target token count in the prompt and constrains generation length.
Such approaches are orthogonal to our method: they control the generation phase, while FIX-2+FIX-4 acts post-generation on already-produced candidates.

\paragraph{Adaptive computation.}
Adaptive computation in neural networks---from early exits \citep{graves2016adaptive} to mixture-of-experts gating---dynamically allocates compute based on input difficulty.
Our failure-trace gating policy can be seen as an adaptive selection layer applied at the output of the frontier generator: it redirects the final answer for a predicted subset of ``weak'' outputs without requiring additional forward passes.

\paragraph{Positioning of this work.}
The present paper contributes a simple, deterministic, gold-free gating policy evaluated under strict reproducibility constraints: exact rule definitions, matched budgets, disjoint evaluation splits, and explicit confidence-interval reporting.
Unlike verifier-based approaches, the method requires no additional model training.
Unlike search-based generation methods, it adds no inference calls after candidate answers and frontier metadata have been produced.
The principal contribution is an empirical demonstration that two lightweight failure-trace signals---the override-reason metadata field and external-consensus agreement---can recover a meaningful fraction of cases where the frontier method's output is unreliable, yielding statistically supported accuracy gains on the tested Cohere setting.
