\section{Experimental Setup}
\label{sec:experiments}

\subsection{Data, model, and protocol}
All main comparisons are conducted on \textbf{Cohere command-r-plus-08-2024} with a fixed per-method budget cap of $B = 6$ logical API calls per example.  The dataset is \texttt{openai/gsm8k}.  Evaluation conditions are matched across all compared candidate-producing methods: every method operates under the same budget cap, provider, and model, so accuracy differences are not confounded by unequal per-method compute.

\medskip\noindent\textbf{Matched-budget definition.} A comparison is \emph{matched-budget} if and only if every compared candidate-producing method is subject to the same maximum logical API call count $B$ per example, with the same provider and model.  No method in the main comparison receives extra calls or a different model.  Failure-Trace Allocator (FTA) is then applied as a post-generation selection policy over the logged candidate answers and frontier metadata.
This contract supports clean method-to-method comparison, but it does not imply total compute parity with a single baseline run when multiple candidate-producing methods are executed together.

\medskip\noindent\textbf{Evaluation role in the paper.}
The matched-budget protocol is part of the contribution because it isolates
answer-source routing from candidate generation. The paper is not evaluating a new
end-to-end solver that spends more compute; rather, it evaluates whether a
post-generation selector can improve final-answer choice when each candidate
producer is held to the same budget contract.

\subsection{Cost and resource usage}
\label{sec:cost}

Table~\ref{tab:cost_budget} reports per-method resource usage measured from logged Aggregate720 runs on Cohere command-r-plus-08-2024. Reported metrics include average logical API calls, average input tokens, average output tokens, and average latency in seconds.  Total tokens (input + output) can be derived by summing the respective columns.  Budget parameter $B = 6$ is shown for completeness.

Failure-Trace Allocator (FTA) adds negligible selection overhead once candidate answers and frontier
metadata are available, but the main deployment cost is candidate-pool construction.
If a deployment must generate frontier, L1, S1, and TALE outputs from scratch, total
wall-clock and API cost depends on which candidate producers are executed and may
exceed a single method's $B=6$ run. In other words, FTA is a zero-extra-call selector
after generation, not a claim of one-run compute equivalence to all baselines combined.
In the logged Aggregate720 runs, the frontier
method has higher average latency than L1, S1, or TALE.
We report cost in logical calls, tokens, and latency; monetary cost depends on provider pricing and is not used as the primary comparison metric.  Dollar-normalized cost analysis, latency percentile distributions, and multi-provider token cost benchmarks are identified as future work (Section~\ref{sec:limitations}).

\subsection{Parameter grounding}
\label{sec:param_grounding}

Table~\ref{tab:param_sensitivity} (Appendix) documents the key parameters and design choices used in Failure-Trace Allocator (FTA), including their values, roles, and the robustness evidence available.  We report parameter grounding and robustness checks rather than a full continuous hyperparameter sweep; a full threshold sweep is left for future work.

\subsection{Primary splits and disjointness}
The primary aggregate (Aggregate720) is formed from three disjoint sources: seed41 main300, seed61 independent120, seed71 final300.  Cross-source overlap checks confirm zero shared example IDs and zero shared question hashes, ensuring that the aggregate evidence is drawn from non-overlapping subpopulations.

\subsection{Statistics}
We report paired bootstrap confidence intervals \citep{efron1993bootstrap} ($n = 5{,}000$ resamples) on final300 and source-stratified aggregate confidence intervals on Aggregate720.  The bootstrap resample count of 5,000 is standard for stable CI estimation at the sample sizes used.  All confidence intervals are two-sided at the 95\% level.  When shown, the \emph{bootstrap positive-delta fraction} is the fraction of bootstrap resamples in which the Failure-Trace Allocator (FTA) delta is positive; it is a descriptive bootstrap summary and should not be interpreted as a classical frequentist $p$-value.

\medskip\noindent\textbf{Offline vs.\ live reproduction.}
The submission package is designed to support offline reproduction of the reported
metrics, paper tables, and bootstrap summaries from processed artifacts without
new provider API calls. Full end-to-end regeneration of raw model outputs requires
commercial provider credentials and live API access, and may differ because of
provider-side nondeterminism, model/version changes, rate limits, or transient
service failures.
