\section{Results and Analysis}
\label{sec:results}

Main results are listed in Table~\ref{tab:main_results} and Figure~\ref{fig:accuracy_ci}.
FIX-2+FIX-4 is the promoted policy; all other FIX variants were evaluated and not promoted
(see Section~\ref{sec:ablation} and Table~\ref{tab:negative_results}).

\paragraph{Final-300.}
On the unbiased 300-example evaluation (seed 71, budget 6), FIX-2+FIX-4 reaches
\textbf{86.67\%} (260/300), versus L1 83.00\% (249/300), S1 82.00\% (246/300),
and TALE 78.33\% (235/300).
Paired bootstrap 95\% confidence intervals (5\,000 resamples) for FIX-2+FIX-4
minus each baseline on this split:
\begin{itemize}[nosep,leftmargin=1.5em]
  \item vs.\ L1: $+3.67$ pp, 95\% CI $[+0.33,\;+7.00]$, bootstrap positive-delta fraction $0.983$
  \item vs.\ S1: $+4.67$ pp, 95\% CI $[+1.00,\;+8.33]$, bootstrap positive-delta fraction $0.993$
  \item vs.\ TALE: $+8.33$ pp, 95\% CI $[+5.00,\;+12.00]$, bootstrap positive-delta fraction $1.000$
\end{itemize}
All three CI lower bounds are strictly positive on this split.

\paragraph{Aggregate-720 (primary).}
The primary claim rests on the disjoint Aggregate-720 evaluation combining three independent
sources (seeds 41, 61, 71; comprising 300, 120, and 300 examples respectively,
with no example-id or question-hash overlap).
FIX-2+FIX-4 reaches \textbf{80.69\%} (581/720), versus L1 77.64\% (559/720),
S1 77.08\% (555/720), and TALE 75.14\% (541/720).
Source-stratified bootstrap 95\% confidence intervals (5\,000 resamples):
\begin{itemize}[nosep,leftmargin=1.5em]
  \item vs.\ L1: $+3.06$ pp, 95\% CI $[+0.83,\;+5.42]$, bootstrap positive-delta fraction $0.995$
  \item vs.\ S1: $+3.61$ pp, 95\% CI $[+1.39,\;+5.69]$, bootstrap positive-delta fraction $0.999$
  \item vs.\ TALE: $+5.56$ pp, 95\% CI $[+3.61,\;+7.50]$, bootstrap positive-delta fraction $1.000$
  \item vs.\ source-local best external: $+3.06$ pp, 95\% CI $[+1.11,\;+5.00]$,
        bootstrap positive-delta fraction $0.999$
\end{itemize}
All aggregate source-stratified CI lower bounds are strictly above zero.
The margin vs.\ best external exceeds 1 pp even at the lower CI bound.

\paragraph{Pooled ensemble baseline.}
We also evaluate a simple pooled answer ensemble over the four already-generated
answers: frontier, L1, S1, and TALE (Table~\ref{tab:pooled_ensemble}).
The primary pooled baseline uses strict majority vote over the four answers and
falls back to the frontier answer for 2--2 ties or all-different cases; this
tie-breaker is deterministic and gold-free.
On Final-300, this Pooled-4 baseline reaches 84.33\% (253/300), while FIX-2+FIX-4
reaches 86.67\% (260/300), a $+2.33$ pp difference with paired bootstrap 95\% CI
$[-0.67,\,+5.67]$.
On Aggregate-720, Pooled-4 reaches 79.86\% (575/720), while FIX-2+FIX-4 reaches
80.69\% (581/720), a $+0.83$ pp difference with source-stratified 95\% CI
$[-1.11,\,+2.78]$.
An external-only L1/S1/TALE majority baseline is even closer: 85.33\% on Final-300
and 80.28\% on Aggregate-720.
Thus, FIX-2+FIX-4 remains ahead by point estimate, but the pooled-ensemble
comparison is not statistically separated and is treated as a robustness check
rather than a promoted superiority claim.
The external fallback order used by FIX-2 is deterministic and fixed for
reproducibility; it is not presented as an optimized learned ranker.  A replay
sensitivity check over alternative external tie orders changes Aggregate-720
FIX-2-only accuracy from 80.00\% to 80.42\%, with frontier fallback on
all-different external ties reaching 80.83\%; these variants are reported only as
sensitivity because they were not the promoted policy.

\paragraph{Source-by-source breakdown.}
Table~\ref{tab:source_by_source} gives the per-source accuracy for all evaluated methods.
Estimates are consistent across sources: FIX-2+FIX-4 leads by point estimate in every
individual source split, with seed-41 showing the smallest advantage
(83.33\% vs.\ 80.33\% for all three baselines) and seed-71 showing the largest
(86.67\% vs.\ 83.00\% for L1).
The seed-61 source is substantially harder in absolute terms: frontier, L1, S1,
and TALE all fall to 57.50\%, 57.50\%, 56.67\%, and 54.17\%, respectively.
The provider/model/budget configuration is unchanged, and the mean question length
is only modestly higher than the other sources (48.5 words vs.\ 46.1 for seed~41
and 44.6 for seed~71).
The available evidence therefore points to source-sample difficulty rather than a
method-specific run configuration change.
FIX-2+FIX-4 still leads the best external on seed~61 by $+1.67$ pp, and the
source-stratified aggregate confidence interval accounts for this source variation.

\paragraph{Win/loss/tie decomposition.}
Appendix Table~\ref{tab:wlt} gives the per-example win/loss/tie counts versus each baseline
on Final-300.
On the Final-300 evaluation, FIX-2+FIX-4 wins on 19 examples vs.\ L1 (losses: 8, ties: 273),
23 examples vs.\ S1 (losses: 9, ties: 268), and 27 examples vs.\ TALE (losses: 2, ties: 271).
The extremely low loss counts vs.\ TALE confirm that the policy's recoveries
substantially outweigh its regressions on this evaluation.

\paragraph{Gate-action decomposition.}
Table~\ref{tab:gate_actions} decomposes the promoted policy into gate actions.
Across Aggregate-720, FIX-2 fires on 122 examples, FIX-4 fires on 5 examples after
FIX-2 does not fire, and no gate fires on 593 examples.
The FIX-4 actions are rare but positive in this artifact: before FIX-4, the
frontier answer is incorrect on all five; after FIX-4, all five are correct.
The same pattern holds on Final-300, where FIX-4 fires on three examples and
contributes three wins, zero losses, and zero ties relative to the frontier answer
and to FIX-2-only replay.

\paragraph{Sensitivity set (supporting diagnostic only).}
Table~\ref{tab:source_by_source} includes a row for a 100-example set (seed~31,
labeled ``sensitivity-only'') that was used as a development diagnostic during
early policy calibration for FIX-1 and FIX-2.
Because this set was involved in parameter selection for earlier FIX variants,
it is excluded from the primary Aggregate-720 evidence and from the bootstrap
confidence intervals reported above.
On this set, FIX-2+FIX-4 achieves 82.00\%, tied with TALE and ahead of L1 (76.00\%)
and S1 (77.00\%).
When the sensitivity set is added to the aggregate ($N = 820$), the positive
point-estimate advantage of FIX-2+FIX-4 over all three external baselines is
preserved, and the overall picture is unchanged.
All promoted accuracy claims in this paper are based on Final-300 and Aggregate-720
only.
