\subsection{Limitations}
\label{sec:limitations}

We first summarize what is established by the current evidence, then state the main boundaries.

\medskip\noindent\textbf{Established in this submission.}
The selective-deferral policy studied here is runtime-legal and gold-free by
construction (Table~\ref{tab:feature_legality}); evaluation is disjoint by design
across the Aggregate-720 sources; and FTA leads each individual external baseline
(L1/S1/TALE) by point estimate with strictly positive source-stratified CI lower
bounds on Aggregate-720. The pooled four-answer comparison is also reported and
shows a closer gap whose CI includes zero.

\medskip\noindent\textbf{Provider-specific scope.}
All main evidence is obtained on Cohere command-r-plus-08-2024. The method is not claimed to generalize to other providers, model families, or API versions without independent replication.

\medskip\noindent\textbf{Benchmark scope.}
Results are scoped to GSM8K (\texttt{openai/gsm8k}) under the matched-budget
answer-selection protocol described in Section~\ref{sec:experiments}. We make no
universal accuracy claim beyond this dataset and task family.

\medskip\noindent\textbf{Budget scope and compute accounting.}
The matched-budget claim is a per-method evaluation contract, not a claim that generating the full frontier/L1/S1/TALE candidate pool costs the same as one method run. We report logical calls, tokens, and latency; monetary cost depends on provider pricing and remains outside the main comparison metric.

\medskip\noindent\textbf{Moderate margin and pooled-baseline caveat.}
The primary gain of FTA over the best external baseline on Aggregate-720 is $+3.06$ percentage points (95\% CI $[+1.11, +5.00]$), while the pooled-four-answer comparison is $+0.83$ pp with CI including zero. These are meaningful but moderate margins that require broader replication.

\medskip\noindent\textbf{Tie-breaker sensitivity.}
The TALE$\succ$S1$\succ$L1 fallback used when all three external answers differ is deterministic and gold-free, but it is not claimed to be optimal. Alternative tie orders move Aggregate-720 replay by less than one percentage point in the available artifacts.

\medskip\noindent\textbf{Residual pool-miss failures.}
A residual failure class exists in which all methods---frontier and external baselines---produce incorrect answers for the same example. The proposed policy cannot recover from this class, as no correct answer is present in the candidate pool.

\medskip\noindent\textbf{Additional evaluated variants.}
Additional cluster-selection, parser, and pool-miss variants were explored during development but did not meet the threshold for inclusion in the final policy. Their implementation labels are retained in Table~\ref{tab:negative_results} for reproducibility.
