\appendix
\section{Reproducibility and Supplementary Material}
\label{sec:appendix_repro}
This appendix collects reproducibility information, additional result decompositions,
parameter grounding, runtime feature legality, and paper-facing name mappings.

\input{tables/tableA1_reproducibility}

\clearpage
\subsection*{Additional Result Decompositions}

The following tables give the per-example win/loss/tie decomposition
(Table~\ref{tab:wlt}) and claim language guidance for manuscript writing
(Table~\ref{tab:claim_language}).

\input{tables/tableA2_win_loss_tie}
\input{tables/tableA3_safe_unsafe_claims}

\clearpage
\subsection*{Parameter Grounding and Sensitivity}

Table~\ref{tab:param_sensitivity} documents the key parameters and design choices
used in FIX-2+FIX-4, including their values, roles, and available robustness evidence.

\input{tables/tableA4_parameter_sensitivity}

\clearpage
\subsection*{Runtime Feature Legality}

Table~\ref{tab:feature_legality} lists all features used by FIX-2+FIX-4 at
inference time and confirms their gold-free status.

\input{tables/tableA5_feature_legality}

\clearpage
\subsection*{Paper-Facing Name Mapping}

Table~\ref{tab:name_mapping} maps paper-facing short names to their
implementation identifiers, roles, runtime availability, and gold-free status.

\input{tables/tableA6_name_mapping}

\section*{Data Availability}
The GSM8K benchmark questions used for evaluation are available from the original source
\citep{cobbe2021training}. A supplementary reproducibility package is included with this
submission. Upon acceptance, the processed evaluation artifacts supporting the reported
tables and figures will be made publicly available in a versioned repository, preferably
with a persistent identifier such as a Zenodo DOI. Additional processed artifacts can be
provided to reviewers upon request.

\section*{Code Availability}
The implementation of the proposed allocator and evaluation scripts will be made publicly
available upon acceptance in a versioned repository, preferably with a persistent
identifier such as a Zenodo DOI. The supplementary reproducibility package included with
this submission contains the processed artifacts needed to inspect the reported results.
Live reruns require provider API access to Cohere command-r-plus-08-2024.

\section*{Funding}
This work was supported by Cohere research API credits. No other specific grant
funding was received from any funding agency in the public, commercial, or
not-for-profit sectors.

\section*{Competing Interests}
The authors declare no competing interests.

\section*{Use of AI Tools}
The author used ChatGPT, Cursor, Claude, GitHub Copilot, Cohere models, and Perplexity AI during parts of the coding, literature-search, manuscript-drafting, editing, and artifact-preparation workflow. These tools were used for assistance with code navigation, implementation support, language editing, reference discovery, and drafting support. All scientific claims, experimental design choices, code changes, analyses, reported results, citations, and final manuscript text were reviewed and approved by the author, who takes full responsibility for the content of the paper.

\section*{Author Contributions}
Soroush Vahidi: Conceptualization, Methodology, Software, Validation, Formal analysis,
Investigation, Data curation, Writing --- original draft, Writing --- review and editing,
Visualization.
