\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{parskip}
\begin{document}

\begin{center}
{\Large \textbf{MLJ Contribution Information Sheet}}\\[4pt]
\end{center}

\section*{Main claim and importance}
FIX-2+FIX-4 is a gold-free, runtime-legal failure-trace-guided allocator for matched-budget LLM reasoning. It improves answer selection by using logged frontier metadata and external consensus signals rather than adding more candidates or using gold labels at runtime.

This matters for machine learning because it studies how to allocate a fixed inference budget more effectively after generation has already happened. The question is not just how to scale compute, but how to choose the best answer from existing model outputs under a strict budget contract.

\section*{Evidence}
\begin{itemize}[leftmargin=*]
  \item Final-300: 260/300 = 86.67\%
  \item Aggregate-720: 581/720 = 80.69\%
  \item Source-stratified bootstrap confidence intervals are positive versus L1, S1, TALE, and the source-local best external baseline.
  \item Non-promoted FIX-5/6/7/8/9 variants are reported as negative or insufficient evidence.
\end{itemize}

\section*{Closest related work}
The manuscript is related to chain-of-thought and self-consistency, test-time compute scaling, budget-forcing / s1-style methods, TALE-style prompt budgeting, tree/graph search, verifier-guided selection, and cost-aware routing. The difference is that this paper operates on runtime-legal frontier and external signals after the budget has already been spent, with no gold labels at decision time.

\section*{Related submission disclosure}
The author will disclose the related NeurIPS-style manuscript under review. That manuscript focuses on broader frontier allocation, STRICT-F3 / STRICT-GATE1-CAP-K6, matched action-budget surfaces, weak anti-collapse, and close top-cluster claims. This MLJ manuscript instead focuses on FIX-2+FIX-4, GSM8K Final-300 / Aggregate-720, L1 / S1 / TALE / source-local best external comparisons, source-stratified bootstrap confidence intervals, and runtime-legal no-gold triggers.

\end{document}
