\section*{Statements and Declarations}

\paragraph{Funding.}
This work was supported in part by research API credits from Cohere, which
supported the main Cohere command-r-plus-08-2024 experiments. CloudRift AI
credits supported preliminary exploratory multi-provider checks reported only
as supporting evidence; they were not used in the primary FTA evaluation. No
other specific grant funding was received from any funding agency in the public,
commercial, or not-for-profit sectors.

\paragraph{Competing Interests.}
The author declares no competing interests.

\paragraph{Ethics Approval.}
Not applicable.

\paragraph{Consent to Participate.}
Not applicable.

\paragraph{Consent for Publication.}
Not applicable.

\paragraph{Data Availability.}
The GSM8K benchmark questions used for evaluation are available from the
original source. A supplementary reproducibility package is included with this
submission and contains the processed evaluation artifacts used to generate the
reported tables and figures, including aggregate summaries, paired comparison
tables, and run manifests. The reported Aggregate-720 accuracy and
confidence-interval tables can be reproduced from these processed artifacts
without issuing new provider API calls. No API keys, credentials, or secrets
are included.

\paragraph{Code Availability.}
The supplementary package includes the code paths and scripts used for policy
replay and evaluation of the reported artifacts. Live regeneration of candidate
answers requires provider API access to Cohere command-r-plus-08-2024; the
reported post-generation analyses are reproducible offline from the supplied
processed artifacts.

\paragraph{Use of AI Tools.}
Generative AI and AI-assisted tools were used during parts of coding, literature
search, manuscript drafting, editing, and artifact preparation. These tools
included ChatGPT, Claude, GitHub Copilot, Cursor, and Perplexity AI.
Cohere command-r-plus-08-2024 was used as an evaluated experimental model in the
reported Cohere/GSM8K experiments rather than as an authoring tool. All
scientific claims, experimental design choices, code changes, analyses,
reported results, citations, and final manuscript text were reviewed and
approved by the author, who takes full responsibility for the content.

\paragraph{Author Contributions.}
Soroush Vahidi: Conceptualization, Methodology, Software, Validation, Formal
analysis, Investigation, Data curation, Writing~--- original draft,
Writing~--- review and editing, Visualization.
