\appendix
\section{Reproducibility and Supplementary Material}
\label{sec:appendix_repro}
This appendix collects reproducibility information, additional result decompositions,
parameter grounding, runtime feature legality, and terminology-to-identifier mappings.

\input{tables/tableA1_reproducibility}

\medskip\noindent\textbf{Reproducibility package contents.}
The submission package is designed to include an anonymous reviewer-access archive
for offline reproduction of the reported summaries. The package contents include
a README or reviewer quickstart, environment or requirements specifications,
configs and run manifests, processed per-example outputs, method summaries,
bootstrap summaries, and scripts that regenerate the reported paper tables and
metrics without new API calls. The package excludes API keys, secrets, \texttt{.env}
files, private credentials, and unrelated local files.

\clearpage
\subsection*{Additional Result Decompositions}

The following tables give the per-example win/loss/tie decomposition
(Table~\ref{tab:wlt}) and claim-scope examples for manuscript wording
(Table~\ref{tab:claim_language}).

\input{tables/tableA2_win_loss_tie}
\input{tables/tableA3_safe_unsafe_claims}

\clearpage
\subsection*{Parameter Grounding and Sensitivity}

Table~\ref{tab:param_sensitivity} documents the key parameters and design choices
used in Failure-Trace Allocator (FTA), including their values, roles, and available robustness evidence.

\input{tables/tableA4_parameter_sensitivity}

\clearpage
\subsection*{Runtime Feature Legality}

Table~\ref{tab:feature_legality} lists all features used by Failure-Trace Allocator (FTA) at
inference time and confirms their gold-free status.

\input{tables/tableA5_feature_legality}

\clearpage
\subsection*{Terminology and Identifier Mapping}

Table~\ref{tab:name_mapping} maps manuscript short names to their
implementation identifiers, roles, runtime availability, and gold-free status.

\input{tables/tableA6_name_mapping}

\section*{Data Availability}
The GSM8K benchmark questions used for evaluation are available from the original source
\citep{cobbe2021training}. This submission is accompanied by a package designed for
anonymous reviewer access and offline reproduction of the reported metrics, tables,
and figures. The processed artifacts in that package include per-example records,
experiment manifests, method summaries, bootstrap summaries, and paper-table
generation outputs; these materials are sufficient to recompute the reported
summary metrics without live model calls. A public archival release of the processed
artifacts will be created upon publication, preferably in a versioned repository
with a persistent identifier.

\section*{Code Availability}
This submission is accompanied by a package designed to include the analysis code,
table-generation scripts, and reproduction instructions needed to recompute the
reported paper metrics from the processed artifacts offline. Full end-to-end
regeneration of raw model outputs requires commercial provider credentials and live
API access to Cohere command-r-plus-08-2024, and may vary because of provider-side
nondeterminism, model/version changes, rate limits, or transient service failures.
No API keys, secrets, \texttt{.env} files, private credentials, or unrelated local
files are included in the reviewer package or any future public release. A public
archival release of the code and processed artifacts will be created upon publication,
preferably in a versioned repository with a persistent identifier.

\section*{Funding}
This work was supported by Cohere research API credits. No other specific grant
funding was received from any funding agency in the public, commercial, or
not-for-profit sectors.

\section*{Competing Interests}
The authors declare no competing interests.

\section*{Use of AI Tools}
The author used ChatGPT, Cursor, Claude, GitHub Copilot, Cohere models, and Perplexity AI during parts of the coding, literature-search, manuscript-drafting, editing, and artifact-preparation workflow. These tools were used for assistance with code navigation, implementation support, language editing, reference discovery, and drafting support. All scientific claims, experimental design choices, code changes, analyses, reported results, citations, and final manuscript text were reviewed and approved by the author, who takes full responsibility for the content of the paper.

\section*{Author Contributions}
Soroush Vahidi: Conceptualization, Methodology, Software, Validation, Formal analysis,
Investigation, Data curation, Writing --- original draft, Writing --- review and editing,
Visualization.
