\documentclass[pdflatex,sn-mathphys-num]{sn-jnl}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{float}
\usepackage{natbib}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric,arrows.meta,positioning}

\begin{document}

\title[Selective Deferral for Budgeted LLM Answer Selection]{Selective Deferral for Budgeted LLM Answer Selection: Failure-Trace Signals under Matched-Budget Evaluation}

\author*[1]{\fnm{Soroush} \sur{Vahidi}}\email{sv96@njit.edu}
\affil*[1]{\orgdiv{Department of Computer Science}, \orgname{New Jersey Institute of Technology}, \orgaddress{\city{Newark}, \state{NJ}, \country{USA}}}

\abstract{%
We study the problem of selecting a final answer from an already generated set of
candidate LLM reasoning outputs under a fixed inference-budget contract. In this
post-generation setting, candidate-producing methods have already spent their
matched per-method budgets, and the remaining question is whether a selector can
choose among their outputs without issuing additional model calls and without
access to ground-truth labels at runtime.
We frame this as \emph{selective deferral} or \emph{answer-source routing} across
candidate producers. We instantiate that framework with \textbf{Failure-Trace
Allocator (FTA)}, a deterministic gold-free policy that routes between a frontier
answer and external answer sources using runtime-observable failure-trace metadata
and cross-candidate agreement features. FTA does not generate new reasoning paths
at selection time. Its first gate, the Low-Depth Guard, defers away from the
frontier when logged metadata indicate a structurally weak single-branch outcome.
Its second gate, the External-Consensus Fallback, defers when three independent
external baselines unanimously disagree with the frontier's selected answer.
Both gates are strictly gold-free: no correctness labels, ground-truth answers,
or example identifiers are accessed at decision time.

We evaluate on the GSM8K benchmark~\citep{cobbe2021training} using
Cohere command-r-plus-08-2024 under a matched per-method budget cap of six
logical inference calls per example.
This budget contract is per candidate-producing method; it is not a claim that
constructing the full frontier+L1+S1+TALE pool from scratch costs one six-call run.
On a disjoint 720-example aggregate spanning three independent evaluation seeds,
FTA achieves 80.69\% accuracy versus 77.64\%, 77.08\%, and 75.14\% for
three independently sourced external baselines (L1, S1, and TALE).
Source-stratified 95\% bootstrap confidence intervals are strictly positive for
all four pairwise comparisons, with the lower bound versus the best external
at $+1.11$ percentage points.
Against a pooled four-answer ensemble (frontier+L1+S1+TALE), treated here as a
strong post-generation aggregation baseline, FTA remains ahead by point estimate
but is not statistically separated on either Final-300 or Aggregate-720.
The empirical evidence is therefore bounded: in the tested Cohere/GSM8K/$B=6$
setting, deterministic trace-guided routing improves over individual baselines and
is competitive with pooled aggregation, but broader generalization requires
independent replication.
}

\keywords{Large language models, answer selection, selective deferral, budgeted inference, test-time compute}

\maketitle

\input{sections/01_introduction}
\input{sections/02_related_work}
\section{Problem Setup and Method}
\label{sec:problem_setup_method}
\input{sections/03_problem_setup}
\input{sections/04_method}
\input{sections/05_experiments}
\input{sections/06_results}

\input{tables/table1_main_results}
\input{tables/table2_source_by_source}
\input{tables/table8_pooled_ensemble}
\input{figures/figure1_method_overview}
\input{figures/figure2_accuracy_ci}

\input{sections/07_ablation}
\input{tables/table3_ablation}
\input{tables/table4_policy_rules}
\input{tables/table9_gate_actions}
\input{tables/table5_cost_budget}

\input{sections/08_failure_analysis}
\input{tables/table6_failure_taxonomy}
\input{figures/figure3_failure_breakdown}

\input{sections/09_discussion}
\input{sections/10_limitations}
\input{sections/11_conclusion}
\input{tables/table7_negative_results}

\section*{Acknowledgements}
The author thanks Professor Ioannis Koutis for his support, guidance, and helpful
discussions during this work. The author is also deeply grateful to his mother for
her continuous support and encouragement. The author acknowledges Cohere for
providing research API credits that supported the model-inference experiments in
this study.

\bibliography{refs}

\clearpage
\onecolumn
\input{appendix}

\end{document}
