\subsection{Ablation Study and Not-Retained Variants}
\label{sec:ablation}

We evaluate ablation and extension variants to test whether the retained two-gate
allocator can be improved by additional routing, extra-action, clustering, parsing,
or pool-miss logic.
Table~\ref{tab:ablation} summarizes the evaluated variants from FIX-1 through FIX-9.
All variants were evaluated via postrun replay on existing candidate artifacts;
no additional inference calls were issued for ablation purposes.
None of the variants met retention criteria beyond Failure-Trace Allocator (FTA, implementation: FIX-2+FIX-4), and they are
reported to delimit the supported claim.

\paragraph{Retained gate components.}
Low-Depth Guard (LDG, implementation: FIX-2) alone achieves 80.00\% on Aggregate-720 ($+2.36$~pp over the frontier
baseline), confirming that the Low-Depth Guard carries most of the combined gain.
External-Consensus Fallback (ECO, implementation: FIX-4) alone achieves 75.00\% on final-300---below Low-Depth Guard (LDG, implementation: FIX-2)---but contributes an
additional $+0.69$~pp when combined with Low-Depth Guard (LDG, implementation: FIX-2), reflecting its role in recovering
cases where Low-Depth Guard (LDG, implementation: FIX-2) does not fire.
FIX-3 (calibration on score-absent non-weak-frontier edge cases) was evaluated but applied to
zero examples in the primary splits, contributing no accuracy change; it is
excluded from the combined policy.

\paragraph{Non-retained variants.}
FIX-5 (TALE-default router) produced zero switches on seeds~41 and~61,
equalling TALE performance on both splits, and only a marginal net positive
switch on seed~71 ($+1$ example over TALE, final-300 78.67\% vs.\ 78.33\%).
This outcome is $-8.00$~pp below Failure-Trace Allocator (FTA, implementation: FIX-2+FIX-4) on the same split.
Note that the Aggregate-720 accuracy for FIX-5 (75.28\%) numerically coincides
with that of the frontier baseline; this reflects the zero-switch behavior on
seeds~41 and~61 (FIX-5 reverts to TALE, and TALE plus the single seed-71 switch
happen to sum to the same total as the frontier), not an equivalence by design.
The TALE-default design assumed a reliable agreement region that did not
materialise consistently across evaluation seeds; see Section~\ref{sec:discussion}
for interpretation.
FIX-6 (extra-action variant) showed a nonnegative pilot signal in the
initial 40-case overlapping evaluation, but an independent 80-case follow-up
yielded net $-1$ for extra frontier actions and net $-4$ for extra TALE
retries relative to Failure-Trace Allocator (FTA, implementation: FIX-2+FIX-4).
Early-stage signal that fails to replicate on disjoint data is the standard
not-retained criterion.
FIX-7 (cluster-level selector) achieved at most $+0.67$~pp in the best rule
variant on final-300, below the threshold for retention in the main method.
FIX-8 (robust parser/canonicaliser) produced zero accuracy-changing switches on
both final-300 and Aggregate-720, indicating that parse-failure residuals are
rare in this evaluation setting.
FIX-9 (pool-miss detector) found 23 of 24 all-methods-wrong residuals to be
generation-limited, with no selector-only remedy available; see the failure
analysis in Section~\ref{sec:failure_analysis}.
