\subsection{Failure Analysis}
\label{sec:failure_analysis}

Table~\ref{tab:failure_taxonomy} and Figure~\ref{fig:failure_breakdown}
classify the 40 residual errors in the Final-300 evaluation by root cause.
Three categories emerge.
\emph{All-methods-wrong} cases (24/40, 60.0\%) are examples where every evaluated
method---the frontier generator and all three external baselines---produced an
incorrect answer.
Because no correct answer appears in the candidate pool, no selection policy can
recover these cases; they represent a hard ceiling for the current approach.
\emph{Parser/canonicalization failures} (12/40, 30.0\%) are cases where the
correct numerical answer was present in the pool but not extracted or matched, due
to format mismatches between the model's output format and the evaluation matcher.
\emph{Present-not-selected} cases (4/40, 10.0\%) are cases where the correct
answer was available in the pool but the Failure-Trace Allocator (FTA, implementation: FIX-2+FIX-4) rule chain did not surface it.

Within the all-methods-wrong category, the dominant subtype is
\emph{multi-step composition traps} (10/24), problems where the error is embedded
in intermediate reasoning rather than in the final answer selection step.
Near-miss numeric errors (5/24), different-wrong-answer divergence with no correct
cluster (4/24), and false consensus (2/24)---where all methods agree on the same
incorrect answer---account for most of the remainder.
False-consensus cases are the most resistant to any selection-based intervention:
unanimous agreement provides no gating signal when the consensus itself is wrong.

These findings directly inform the scope of Failure-Trace Allocator (FTA, implementation: FIX-2+FIX-4) and the directions for
future work.
The all-methods-wrong class (60\% of failures) is generation-limited: addressing it
requires either stronger base generators or training-time interventions that improve
coverage of hard compositional patterns, not better post-hoc selection policies.
The parser/canonicalization class (30\% of failures) is potentially tractable with
improved answer normalization; however, the FIX-8 prototype produced zero
accuracy-changing switches in this setting, suggesting the problem is subtler than
simple string-matching improvements.
The present-not-selected class (10\% of failures) represents the only residual
opportunity that a selection policy could in principle address without improved
candidate generation.
