\section{Discussion}
\label{sec:discussion}

\paragraph{Why failure-trace-guided gating works.}
The two gates in FIX-2+FIX-4 target failure modes that are identifiable at runtime
without any access to gold labels.
The Low-Depth Guard (FIX-2) addresses a structural weakness: when the frontier search
terminates with a \textit{single weak branch}---signalled by the \texttt{override\_reason}
field---the resulting answer is drawn from a narrow slice of the candidate space.
In such cases, the external majority vote is empirically more reliable.
The External-Consensus Fallback (FIX-4) targets a different pattern: when the frontier
selects its own answer confidently (\texttt{direct\_frontier\_agree}) yet all three
independent external baselines unanimously prefer a different answer, that unanimous
disagreement constitutes strong evidence that the frontier is wrong.
Both signals are available as logged metadata from normal frontier execution;
no additional inference or labelling is required.

\paragraph{Why the non-promoted variants were abandoned.}
FIX-5 (TALE-default router) produced zero switches on seeds~41 and~61,
equalling TALE performance exactly on both splits (80.33\% and 54.17\%,
respectively).
On seed~71 (Final-300), FIX-5 made one net positive switch over TALE
(78.67\% vs.\ 78.33\%), a difference of a single example that is negligible
compared to the $+8.33$~pp advantage of FIX-2+FIX-4 over TALE on the same split.
The TALE-default design assumed a reliable agreement region that did not materialise
consistently across evaluation seeds, making the router effectively inactive in most
conditions.

FIX-6/LoVEC proposed collecting extra frontier or TALE-retry actions for predicted
failure cases.
The first 40-case overlapping pilot showed nonnegative action-value signal, but
the independent 80-case Stage-2 relaunch (disjoint from the pilot) yielded
net $-1$ for extra frontier actions and net $-4$ for extra TALE retries relative to FIX-2+FIX-4,
with non-trivial control-slice regressions (8.9\% for frontier, 11.1\% for TALE retry).
The failure to replicate on disjoint data is the key indicator: the pilot signal
appears to have been artefact-specific rather than generalisable.

FIX-7 (cluster-level selector) and FIX-8 (robust parser/canonicaliser) both produced
zero accuracy-changing switches on the final-300 and aggregate-720 evaluations.
Their logged action counts confirm that the targeted failure patterns---ambiguous answer
clusters and parse-failure residuals---are rare in the current evaluation setting,
leaving no headroom for these rules to operate.

\paragraph{How aggregate-720 changes the evidence posture.}
The most substantive evidence shift in this work is the transition from a single-run
300-example evaluation (seed 41, where the CI lower bound vs.\ L1 still crossed zero
at $[-0.48, +5.71]$) to the disjoint Aggregate-720 evidence (seeds 41, 61, 71).
By combining three independently sampled unbiased evaluation splits, the stratified
bootstrap CI narrows sufficiently that the lower bound vs.\ every external baseline
is strictly positive.
This is not simply a power argument: the source-stratified design controls for
seed-specific variance, and the zero-overlap check on example-id and question-hash
confirms independence.
The result is that the point-estimate advantage of FIX-2+FIX-4 is consistent across
all three seeds, which is the primary reason the aggregate CIs no longer include zero.

\paragraph{Evidence scope and generalization.}
The transition from single-seed to multi-seed aggregate evidence is the key
methodological contribution of this evaluation.
On seed~41 alone, the CI versus L1 crossed zero ($[-0.48, +5.71]$); on the
source-stratified Aggregate-720, the same comparison yields CI $[+0.83, +5.42]$.
This narrowing is not merely a power argument: the source-stratified design
controls for seed-specific variance, and the consistency of positive point estimates
across all three seeds confirms that the advantage is not an artefact of a
single evaluation draw.
What this evidence does \emph{not} establish is generalization beyond the tested
scope: whether the same failure-trace signals are informative on other providers,
benchmarks, or budget levels is an open empirical question.
Section~\ref{sec:limitations} enumerates the scope boundaries explicitly.
