% Manuscript insertion: main results claim-safety statistical table paragraph
\paragraph{Claim-safety statistical evidence.}
To make uncertainty explicit, we include a paper-facing paired/bootstrap/permutation summary (Table~\ref{tab:claim_safety_statistical_tests}; generated from \texttt{outputs/paper_tables/table\_claim\_safety\_statistical\_tests.tex}). Across matched-surface slices, Strict-F3 vs Strict-Gate1-Cap-K6 is fragile/non-decisive; no central claim in this paper depends on a decisive ranking between these two variants. Our main-text interpretation is therefore family-level: leading frontier-allocation variants are statistically close and surface-dependent, while the stronger mechanism evidence is the consistent role of branch-level allocation and early tree-shape bottlenecks (especially absent-from-tree failures).

\paragraph{Anti-collapse calibration note (Figure~7 / ablation consistency).}
The strict-F3 component-ablation pattern is non-monotonic: removing the default anti-collapse term improves performance on the original paper surface. A targeted six-seed calibration sweep resolves this contradiction as a calibration tradeoff rather than a component-wise validation result: weak anti-collapse is best (\(0.6407\)), off also exceeds default (\(0.6241\) vs \(0.5972\)), strong is near-default (\(0.5991\)), and conditional underperforms (\(0.5861\)). We therefore describe anti-collapse as a calibration-sensitive answer-distinct preservation design axis, while using repeat-expansion moderation and answer-support aggregation as safer component evidence anchors.

\paragraph{Real-model appendix boundary (Cohere Stage-1 decision package).}
Real-model evidence is not used as main-text superiority support. The Cohere Stage-1 decision package reports an unfavorable paired comparison against \texttt{external\_l1\_max} (matched \(n=30\), strict-F3 accuracy \(0.5333\) vs \(0.8000\), paired delta \(-0.2667\), bootstrap 95\% CI \([-0.4667,-0.0667]\), and cost-normalized metrics favoring \texttt{external\_l1\_max}). We therefore keep real-model material as appendix diagnostics/calibration and do not claim real-model dominance.
